\prefacesection{Acknowledgments}

% Advisor
First of all, I am deeply indebted to my advisor,
Percy Liang,
who has been amazingly supportive throughout my whole Ph.D.\ career.
Percy's academic excellence needs no introduction,
and by being his advisee,
I learned that Percy's work ethics,
time management,
lateral thinking,
expertise in numerous research areas,
and communication skills all contributed to his success.
I was lucky to be among the first students in Percy's group,
meaning that I had an opportunity to received a lot of advice from him,
both in academic and personal matters.
Percy was also one of the most patient and understanding person
I have ever met,
and I do not think I can sanely survive the Ph.D.\ program
without him.
%Percy also instilled in me how to look at research problems
%in different perspectives,
%and to effectively communicate the results to the audience.
I am extremely grateful for the time and effort Percy dedicated
to support me,
and I would like to thank him from the bottom of my heart.

% Thesis committee
I would also like to thank my dissertation committee
for their guidance and suggestions.
First, I am grateful to Chris Manning for
being a great runner of the Stanford NLP community
and an advisor for my first-year rotation project.
I also learned a lot from his information retrieval course
while I was working as a course assistant.
Next, I want to thank Dan Jurafsky for his
support and advice throughout my career.
His textbook also plays an important role
for the content in this dissertation.
I want to thank Chris R\'e for asking critical
questions during the oral defense
and directing me to the work on information extraction.
Finally, I want to thank Chris Potts
for agreeing to be the
oral committee chair
and for his great suggestions during the defense.

% Coauthors
During the past six years,
I had great pleasure of working with
many amazing colleagues and coauthors.
For the work presented in this dissertation,
I would like to especially thank
Kelvin Guu and Evan Liu for being my friends and collaborators
on various projects over the last three years;
Yuchen Zhang for the work on macro rules;
Allan Jiang and Tim Shi for the work on web interaction;
and Reggy Long for for the work on sequential semantic parsing.
I would like to also thank my collaborators on other projects
at Stanford University:
Jonathan Berant,
Kartik Chandra,
Robin Jia,
Ramtin Keramati,
Jason Koenig,
Sumith Kulal,
Mina Lee,
Oded Padon,
Sudarshan Seshadri,
Megha Srivastava, and
Sida Wang.
I also want to extend my gratitude to Alex Aiken and Emma Brunskill
for supervising me on my joint projects outside this dissertation.

% Funding and organization
The research presented in this dissertation
would not exist without the funding by the following organizations:
Amazon,
Defense Advanced Research Projects Agency (DARPA),
Google,
Microsoft,
National Science Foundation (NSF),
and Tencent.

% Work at other places
My research experience was also shaped by the research internships
during my Ph.D.\ years.
I would like to thank Asli Celikyilmaz,
Dilek Hakkani-T\"ur,
and Gokhan T\"ur
for my internship at Microsoft Research;
Arne Mauser and Jakob Uszkoreit
for my internship at Google;
and Arash Einolghozati, Sonal Gupta, 
Mike Lewis, Karishma Mandyam, 
Mrinal Mohit, Rushin Shah, and Luke Zettlemoyer
for my internship at Facebook.

% Friends
I am also thankful for my marvelous friends:
everyone at the Stanford Natural Language Processing Group,
who were extremely friendly and supportive
even during the tightest deadlines;
and all my friends at the Stanford Thai Student Association,
who taught me life skills and gave me a space to socialize.
I want to especially thank
Anak Yodpinyanee for sparking my interest in natural language processing;
Pramook Khungurn for giving me advice on academic matters;
and
Warut Suksompong for hanging out with me
and being a great friend
during the past 10+ years.

% Family
Finally, I would like to express my gratitude to my family
for raising me and giving me emotional supports throughout my life.
Words cannot describe how much my father, my mother, and my sister
mean to me and how much I appreciate them.
